Long groovy title goes here

### 2013-06-27 shanghai.tex
Superficial changes, mostly notes to myself

  To see why this is so, consider the category \cdef{$\CS_0(G)$} of
  pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$
  and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ satisfies
  condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$
  are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}.
  \David{Should we move this definition since it will be important elsewhere?}
  Let $b : \bG \to G$ be base change
  (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$).
  The proof of Proposition~\ref{prop:pullback} adapts
  (simplifies, in fact) to show that $b^* : \CS_0(G) \to \CS(G)$ is a
  monoidal functor. This functor is fully faithful; see
  \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.  We will
  show that $b^*$ is essentially surjective.

@@

@@

\begin{remark}
  We have seen that if $f : H\to G$ is a finite etale cover of $G$ by
  a smooth group scheme and if all geometric automorphisms of $f$ are
  fixed by Frobenius, then every character of $\ker f$ determines a
  character sheaf on $G$. However, it is not true that every character
  sheaf on $G$, in the sense of Section~\ref{sec:category} arises not
  all character sheaves on $G$ arise in this manner.
\end{remark}
%\input{centralextensions}

@@

%\input{application}
\begin{theorem}\label{thm:application}
  Let $T$ be an algebraic torus over a non-Archimdean local field $K$.
  Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d \in \ZZ_{>0}$, the
  Picard group of the category of character sheaves on $\GN{T}_d$ is
  canonically isomorphic to the group of characters of $T(K)$ of depth
  less than $d$:
  \[
  \CSiso{\GN{T}_d} \iso \Hom_{< d}(T(K),\EEx).
  \]
\end{theorem}

@@

\Clifton{Explain what happens as $d\in \NN$ varies.}
Suppose $d\leq d'$.

@@

\Clifton{Prove that $\GN{T}$ is a scheme? Strictly speaking, we don't
  care about \ref{scheme}.}
\begin{proposition}
  Fundamental properties of $\GN{T}$:
  \begin{enumerate}
  \labitem{(GN.0)}{scheme} $\GN{T}$ is a commutative group scheme over $\Fq$;
  \labitem{(GN.1)}{T(K)} $\GN{T}(\Fq) = T(K)$, canonically.
  \end{enumerate}
\end{proposition}

>>>>

  To see why this is so, consider the category \cdef{$\CS_0(G)$} of
  pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$
  and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ satisfies
  condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$
  are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}.
  \David{Should we move this definition since it will be important elsewhere?}
  \Clifton{Agreed. I'll do that.}
  Let $b : \bG \to G$ be base change
  (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$).
  The proof of Proposition~\ref{prop:pullback} adapts
  (simplifies, in fact) to show that $b^* : \CS_0(G) \to \CS(G)$ is a
  monoidal functor. This functor is fully faithful; see
  \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.  We will
  show that $b^*$ is essentially surjective.

@@

\Clifton{I'm going to remove all mention of line bundles from this paper.}

@@

\begin{remark}
  We have seen that if $f : H\to G$ is a finite etale cover of $G$ by
  a smooth group scheme and if all geometric automorphisms of $f$ are
  fixed by Frobenius, then every character of $\ker f$ determines a
  character sheaf on $G$. However, it is not true that every character
  sheaf on $G$ arises in this manner.
\end{remark}
\Clifton{I can flesh out this remark once I've promoted the definition of $\CS_0(G)$ (category of bounded character sheaves on $G$).}
%\input{centralextensions}

@@

%\input{application}
\begin{theorem}\label{thm:application}
  Let $T$ be an algebraic torus over a non-Archimedean local field $K$.
  Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d \in \ZZ_{>0}$, the
  Picard group of the category of character sheaves on $\GN{T}_d$ is
  canonically isomorphic to the group of characters of $T(K)$ of depth
  less than $d$:
  \[
  \CSiso{\GN{T}_d} \iso \Hom_{< d}(T(K),\EEx).
  \]
\end{theorem}

@@

\Clifton{Explain what happens as $d$ varies.}
Suppose $d\leq d'$.

@@

\Clifton{Prove that $\GN{T}$ is a scheme? Strictly speaking, we don't
  care about \ref{scheme}.}

\Clifton{Must still define $\CS(\GN{T})$, since it is not an instance
 of our definitions, above.}

\begin{proposition}
  Fundamental properties of $\GN{T}$:
  \begin{enumerate}
  \labitem{(GN.0)}{scheme} $\GN{T}$ is a commutative group scheme over $\Fq$;
  \labitem{(GN.1)}{T(K)} $\GN{T}(\Fq) = T(K)$, canonically.
  \end{enumerate}
\end{proposition}
